---
title: "projectC"
author: "Phoebe Hessen"
date: "5/1/2020"
output: pdf_document
---

# Libraries

```{r}
library(tidyverse)
library(caret)
library(parallel)
library(doParallel)
```


# Data Import and Cleaning

```{r}
data <- read_csv("data/tr_survey.csv") %>%
  select("Motivated", "Flexibility":"Reward - Importance")

set.seed(123)

# Creating random train and holdout samples
rows <- sample(nrow(data))
shuffled_data <- data[rows,]
train <- shuffled_data[51:nrow(shuffled_data),]
holdout <- shuffled_data[1:50,]

# Creating a training method vector to do 10-fold cross-validation
index <- createFolds(train$Motivated, k = 10, returnTrain = T)
my_control_train <- trainControl(method = "cv", number = 10, index = index, verboseIter = T)

# Creating a pre-processing vector to use for all models that imputes missing
# values using the knn technique, centers and scales the data, and removes
# predictors with near zero variance
my_preProcess <- c("knnImpute","zv", "center", "scale")
```


This dataset was collected by myself and some colleagues when I was working as
an HR Intern at Thomson Reuters. It contains demographic information and self-
reported job characteristics and the importance of those characteristics from
members of the Legal division Sales team. I chose this dataset because it 
contains interesting information, and is well-suited to machine learning (as
described below).

I am interested in predicting self-reported motivation at work ("Motivated")
based on self-reported job characteristics and their importance to the 
employee. Machine learning is appropriate in this scenario because I
believe that there may be an interaction between the ratings of the extent to
which a job contains a certain characteristic (e.g., has advancement 
opportunities) and how important those characteristics are to an employee (e.g.
importance of advancement opportunities) in predicting motivation at work. 
Therefore, the original proposed model will include all two-way interactions.
With a sample size of only 249, traditional regression methods will not be 
appropriate in a model with 171 predictors. Machine learning is a better option.
A model developed in this manner could help predict who may lack motivation 
based on their self-reports of job characteristics and associated importance.

Given that I am predicting a quantitative outcome, with a small sample size
where potentially many of the predictors (i.e., many of the two-way interactions
in particular) may not be important, I have elected to use elastic net 
regression. This will allow predictors that are not important to either be
weighted very lightly or even drop out of the model entirely (depending on the
hyperparameters selected). 


# Analysis and Visualization

```{r}
local_cluster <- makeCluster(detectCores()-1)
registerDoParallel(local_cluster)

mod <- train(
  Motivated ~ . ^2, 
  train,
  method = "glmnet",
  preProcess = my_preProcess,
  na.action = na.pass,
  trControl = my_control_train,
  tuneLength = 7
)

stopCluster(local_cluster)
registerDoSEQ()
```

The optimal model that resulted had alpha = 1 and lambda = 0.0461. This means
that it is a LASSO regression model, which further means that unimportant 
predictors could be dropped from the final model. 


```{r}
mod_predict <- predict(mod, holdout, na.action=na.pass)
correlation <- cor(holdout$Motivated, mod_predict)
correlation
```

The correlation between the training sample and the holdout sample is 
`r correlation`. This is a fairly good correlation, indication that motivation
can be predicted by this set of job characteristics and their importance 
ratings. 

```{r}
plot(mod$finalModel)
coef(mod$finalModel, mod$bestTune$lambda)
```

From both the plot of the coefficients and the list of coefficients, a couple 
things are apparent. There are many coefficients that are driven down to zero
or near zero vlaues. However, there are also several predictors that turn out 
to be important for predicting motivation. For example, the main effects of
Impact (feeling like the work you do makes an impact) and Appreciation (feeling
appreciated for the work you do), along with 11 of the interaction terms, 
appear to contribute significantly to the prediction of motivation at work. 
Based on this, it appears that the level of motivation one experiences at work
is related to one's perceptions of the presence (or absence) of various job 
characteristics and their importance.  




